Aa Language Reference Manual

### 2016-06-19 v2/Ahir-asm/devel/docs/AaLRM.tex
Added decode, encode, bitreduce operators to Aa.

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Slice expressions.
\item Bitmap (bit permutation) expressions.
\item Binary expressions.
\item Ternary expressions.
\end{itemize}

@@

>>>>

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Useful Unary logical expressions.
\item Slice expressions.
\item Bitmap (bit permutation) expressions.
\item Binary expressions.
\item Ternary expressions.
\end{itemize}

@@

\subsection{Useful Unary Logical expressions}

Some very useful logical building blocks are decoders,
encoders and bit-reduction operators.

\begin{itemize}
\item The unary expression
\begin{verbatim}
($encode x)
\end{verbatim}
expresses the encoded version of $x$ (produces a \$uint 
whose length is $\log{length(x)}$).  It operates only on \$uint types,
and produces an encoding of $x$ under the assumption that only
one of the bits in $x$ is $1$.
\item The unary expression 
\begin{verbatim}
($p_encode x)
\end{verbatim}
expresses the priority-encoded version of $x$ (produces a \$uint which
whose length is $length(x)$).  It operates only on \$uint types,
and identifies the highest bit position of $x$ which is $1$. For example
if $x$ is $01010$, then the expression will evaluate to $01000$.
\item The unary expressions
\begin{verbatim}
($bitreduce | x)
($bitreduce & x)
($bitreduce ^ x)
\end{verbatim}
produce the reduced single-bit version of $x$ with the specified operation.
For example, the bit-reduced OR is the OR of all the bits of $x$.
\end{itemize}
